Presentation Title

### 2017-08-22 thesis/chapters/ch6-conclusion.tex
Edit grammar etc.

In this work we introduced an application neutral blockchain system which we call \textsc{Checo}.
We add checkpoint block to the existing TrustChain data structure to capture the system state.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result, which is a set of checkpoint blocks, lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

@@

Our experiment is carried out in a somewhat idealised world (DAS-5).
We hope to experiment our prototype in a more realistic environment.
For example, DeterLab~\cite{mirkovic2012teaching} lets users simulate network delay,
which is important for discovering issue that may only occur in hostile environments.
To understand our system further, we hope to experiment with a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the standard TrustChain in Tribler is used for accounting internet traffic between users,
but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly, it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

The fault tolerance property is adequate for permissioned systems where nodes have relatively more trust between each other.
However, it is not adequate for permissionless systems,
which usually aim to tolerate fault that involve a minority of the network,
which can be just shy of 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme (e.g., Ouroboros~\cite{kiayias2017ouroboros}) which means that nodes with more stake in the system get more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stake holders are honest.

Finally, as mentioned in~\Cref{sec:permissionless}, we wish to evaluate our system (analytically and experimentally) in the permissionless settings.
This would enable our protocol to be applied to a much wider range of applications.

>>>>

In this work, we introduced an application neutral blockchain system which we call \textsc{Checo}.
We add checkpoint block to the existing TrustChain data structure to capture the system state.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result, which is a set of checkpoint blocks, lets nodes elect new facilitators and create new checkpoint blocks.
The existing work on True Halves is formalised to act as our transaction protocol.
Finally, we introduce a validation protocol which ensures that if agreed fragments for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

@@

Our experiment is conducted in a somewhat idealised world (DAS-5).
We hope to study our prototype in a more realistic environment.
For example, DeterLab~\cite{mirkovic2012teaching} lets users simulate network delay,
which is essential for discovering issues that may only occur in hostile environments.
To understand our system further, we hope to experiment with a real platform with real users such as Tribler~\cite{pouwelse2008tribler}.
For instance, the standard TrustChain in Tribler is used for accounting internet traffic between users,
but it has no global consensus.
It would be useful to integrate our consensus protocol into Tribler to prevent misreporting attacks.
More importantly, it gives us an opportunity to observe the characteristics of our system in the real world and how it evolves with new features or alterations.

The fault tolerance property is adequate for permissioned systems where nodes have relatively more trust between each other.
However, it is not adequate for permissionless systems,
which usually aim to tolerate fault that involves a minority of the network,
which can be just shy of 50\%.
For future work, we propose the following two ways to improve fault tolerance.
First, use a reputation mechanism to select facilitators rather than simply selecting them randomly so that faulty nodes are less likely to be selected.
This technique of course heavily depends on the application,
for P2P file sharing systems the reputation score may be the number of bytes contributed to the network.
Second, instead of using ACS we use a proof-of-stake (PoS) scheme (e.g., Ouroboros~\cite{kiayias2017ouroboros}) which means that nodes with more stake in the system get more vote.
In an ideal PoS scheme, the system can tolerate any fault if the majority of the stakeholders are honest.

Finally, as mentioned in~\Cref{sec:permissionless}, we wish to evaluate our system (analytically and experimentally) in the permissionless settings.
It would enable our protocol to be applied to a much wider range of applications.

### 2017-08-22 thesis/formalities/abstract.tex
Edit grammar etc.

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution,
where performance increases by adding more nodes to the system,
blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains a personal hash chain,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the personal hash chains,
thus a single checkpoint block may represent an arbitrarily large set of transactions.
We introduce a validation protocol so that any node can check the validity of any transaction.
Since it is a point-to-point protocol, we achieve horizontal scalability.
% how good is the solution?
We analytically evaluate our system and proof a number of highly desirable correctness properties.
Further, we give a free and open-source implementation of \textsc{Checo} and evaluate it experimentally.
Our results show a strong indication of horizontal scalability.
\end{abstract}

>>>>

\begin{abstract}
% what's the problem?
Blockchain systems have the potential to decentralise many traditionally centralised systems.
However, scalability remains a key challenge.
Without a horizontally scalable solution,
where performance increases by adding more nodes to the system,
blockchain systems remain unsuitable for ubiquitous use.
% what's the solution?
We design a novel blockchain system called \textsc{Checo}.
Each node in our system maintains a personal hash chain,
which only stores transactions that the node is involved in.
A consensus is reached on special blocks called checkpoint blocks rather than on all the transactions.
Checkpoint blocks are effectively a hash pointer to the personal hash chains;
thus a single checkpoint block may represent an arbitrarily large set of transactions.
We introduce a validation protocol so that any node can check the validity of any transaction.
Since it is a point-to-point protocol, we achieve horizontal scalability.
% how good is the solution?
We analytically evaluate our system and proof a number of highly desirable correctness properties.
Further, we give a free and open-source implementation of \textsc{Checo} and evaluate it experimentally.
Our results show a strong indication of horizontal scalability.
\end{abstract}

### 2017-08-22 thesis/formalities/preface.tex
Edit grammar etc.

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, the time when I mined my first Bitcoin, 
I became cautious of the security and privacy issues surrounding centralised systems
and became interested in building a decentralised society.
Following the Snowden revelations, the interest became a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my personal ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.

@@

\noindent
There are a number of people who have supported me in this endeavour who I would like to thank.
My supervisor Dr. Johan Pouwelse, your unrivalled enthusiasm and guidance have kept me motivated and productive.
Dr. Zhijie Ren, this work would not have been possible without your invaluable input and the numerous discussions which we have had.
Prof. Dick Epema, you taught me a lot on report writing and the use (and misuse) of mathematical formalism.
Members of the Tribler team---Martijn de Vos, Quinten Stokkink and Chengxin Ma,
you have my gratitude for helping me with the implementation and proofreading my work,
and of course the free coffee.
Members of the Cyber Security group---Dr. Zekeriya Erkin and O\u{g}uzhan Ersoy,
I thank both of you for your feedback on my presentations.

>>>>

\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
Since early 2013, the time when I mined my first Bitcoin, 
I became cautious of the security and privacy issues surrounding centralised systems
and became interested in building a decentralised society.
Following the Snowden revelations, the interest grew into a desire that has stayed with me ever since.
Today, many blockchain systems are mature, but still not yet ready for ubiquitous use due to the scalability limitation.
Many of us still do not use Bitcoin to purchase everyday goods, online or offline.
This limitation, as well as my ambitions, led me to this thesis,
with the goal of creating a truly horizontally scalable solution.

@@

\noindent
Many people have supported me in this endeavour which I would like to thank.
My supervisor Dr Johan Pouwelse, your unrivalled enthusiasm and guidance have kept me motivated and productive.
Dr Zhijie Ren, this work would not have been possible without your invaluable input and the numerous discussions which we have had.
Prof Dick Epema, you taught me a lot about report writing and the use (and misuse) of mathematical formalism.
Members of the Tribler team---Martijn de Vos, Quinten Stokkink and Chengxin Ma,
you have my gratitude for helping me with the implementation and proofreading my work,
and of course the free coffee.
Members of the Cyber Security group---Dr Zekeriya Erkin and O\u{g}uzhan Ersoy,
I thank you both for your feedback on my presentations.
